\section{Task 2: LP and MILP Formulation}
\label{sec:task2}
This section answers assignment Task 3.2. The full mathematical model is given once in Section~\ref{sec:model}; this task explains how it is used computationally.

\subsection{MILP Formulation}
\label{sec:task2-milp}
The model is a mixed-integer linear program because all balances, colour constraints, quality constraints, and process-linking constraints are linear, while $z_{\mathrm{malt}}$ and $z_{\mathrm{mash}}$ are binary. The two binary variables determine whether fixed malting and mashing costs are charged.

\subsection{LP Relaxation}
\label{sec:task2-relaxation}
The relaxed model uses the same equations as the MILP but replaces the binary restrictions by
\begin{equation}
  0 \leq z_{\mathrm{malt}}, z_{\mathrm{mash}} \leq 1.
\end{equation}
For cost minimisation, this gives a lower bound on the MILP optimum. A relaxed solution may contain fractional process variables, so it is not necessarily a valid production plan.

\subsection{Brute-Force Method}
\label{sec:task2-bruteforce}
Enumerating the binary variables is exact in this project because there are only two process choices and only three valid combinations:
\[
(z_{\mathrm{malt}},z_{\mathrm{mash}})\in\{(0,0),(0,1),(1,1)\}.
\]
For each combination, the binary variables are fixed and the remaining continuous LP is solved. The best feasible solution among these LPs is the original MILP solution.

\subsection{Programmatic Implementation}
\label{sec:task2-implementation}
The implementation is written in Python. The helper file \texttt{brew\_utils.py} reads \texttt{dataset\_EN.txt}, defines the conversion constants, and provides calculation helpers. Each notebook builds the vector $c$, equality matrix $A_{\mathrm{eq}}$, inequality matrix $A_{\mathrm{ub}}$, right-hand sides, and variable bounds for \texttt{scipy.optimize.linprog}. More advanced LP or MILP solvers are not used. Result tables report only non-zero decision variables rather than the full optimisation vector.

% task_32.ipynb contains the matrix-building implementation and the demonstration solve.
